The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-03-23 SC-challenge.tex
adding Kyle's suggested workshop URLs

\knnote{mention workshops on software citation; University of Manchester (? can't actually find that one). Additional references are good.} \katznote{\url{https://softwaredatacitation.org/}  \url{http://www.software.ac.uk/software-credit} maybe \url{http://software.ac.uk/maintainable-software-practice-workshop}} \katznote{Arfon, are the more that showed up in related work in the software citation activity?}

>>>>

\knnote{mention workshops on software citation; University of Manchester (? can't actually find that one). Additional references are good.}

\katznote{Some ideas: \\
\url{https://softwaredatacitation.org/} \\
\url{http://www.software.ac.uk/software-credit}  \\
\url{http://astronomy-software-index.github.io/2015-workshop/} \\
\url{https://geodynamics.org/cig/projects/saga/} \\
maybe \url{http://software.ac.uk/maintainable-software-practice-workshop}}

\katznote{Arfon, are the more that showed up in related work in the software citation activity?}
